---
title: "Test your skills"
author: "Original by Greg Wilson (adopted for teaching by Thomas Koentges)"
date: '2021-05-27'
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
```

The file `toronto-covid-2021-01-04.csv` contains reports of COVID-19 cases in Toronto.
Load this file to create a tibble called `covid`.

```{r read_data}
covid <- read_csv("toronto-covid-2021-01-04.csv")
```

Convert the values in the `gender` column to lower case; replace all "unknown" gender entries with `NA`; and then convert the entire column to a factor.
Do not overwrite `covid`, but instead display the result inline.

```{r unknown_as_na}
covid %>%
  mutate(gender = ifelse(gender == "UNKNOWN", NA, str_to_lower(gender)),
         gender = as_factor(gender))
```

Use `covid` to calculate the ratio of the number of patients who are currently hospitalized to the number of patients who have ever been hospitalized.

```{r hospitalized_ratio}
covid %>% 
  select(currently_hospitalized, ever_hospitalized) %>%
  mutate(across(everything(),
                ~ case_when(. == "No" ~ 0,
                            . == "Yes" ~ 1))) %>%
  summarise(across(everything(), sum)) %>%
  mutate(ratio = currently_hospitalized / ever_hospitalized) %>% 
  pull(ratio)
```

Use `covid` to create a summary showing the number of confirmed reports per month in 2020.

```{r confirmed_monthly_2020}
covid %>% filter(year(reported_date) == 2020 & classification == "CONFIRMED") %>%  mutate(month = month(reported_date, label = T)) %>% count(month)
```

Construct a model showing how well the number of cases reported in one month predicts the number of cases reported in the next month.
(You may find the `lag()` function useful.)

```{r correlation}
covid %>% mutate(month = month(reported_date, label = T)) %>% count(month) %>% mutate(last_month = lag(n), this_month = n) %>% ggplot(aes(last_month, this_month)) + geom_smooth()
```

Create a stacked bar chart with the age groups on the X axis showing the fraction of cases of each source. Facet the plot by gender:

```{r stacked_bar_faced}
covid %>%
  ggplot() + geom_bar(aes(age_group, fill = source)) + facet_wrap(~gender)
```


Count the number of days in 2020 in which the number of reported cases was higher than the number reported the day before.

```{r days_of_increase}
covid %>% 
  filter(year(reported_date) == 2020) %>% 
  count(reported_date) %>% 
  mutate(day_before = reported_date - days(1)) %>% 
  inner_join(covid %>% 
               filter(year(reported_date) == 2020) %>%
               count(reported_date) %>% 
               rename(day_before = reported_date, cases_before = n)) %>%
  filter(n > cases_before) %>% 
  nrow
```

Create a new tibble called `history` showing the number of cases per month for each postal code prefix.
You may display the month using its full name (e.g., "September") or as a number (e.g., "09").

```{r create_history}
history <- covid %>% 
  mutate(month = month(reported_date, label = T, abbr = F)) %>% 
  count(postal_code_prefix, month)
```

Rearrange the table you just created so that it has 13 columns: one called `postal_code_prefix` and one more for each month.
The first value in each row must be a postal code prefix;
the other values in that row must be the number of cases in that region and that month,
and missing values must be shown as 0 rather than NA.
Again, you may display the month using its full name or as a number.

```{r rearrange_table}
history %>% 
  pivot_wider(names_from = month, values_from = n, values_fill = 0)
```

The file `classification.xlsx` classifies age ranges into four groups.
Read this file to create a tibble called `classification`.

```{r read_data_xlsx}
library(readxl)
classification <- read_excel("classification.xlsx")
```

Use this tibble and the `covid` tibble to create a new tibble with one column containing the age classification, one called `earliest_reported` showing the first date of a report for that age group, and one called `largest_delay` showing the largest difference (in days) between the episode date and the reported date within that age group.

```{r summarize_classified}
covid %>% 
  group_by(age_group) %>% 
  select(age_group, episode_date, reported_date) %>% 
  mutate(delay = (episode_date %--% reported_date) / days(1)) %>%
  summarise(largest_delay = max(delay), earliest_reported = min(reported_date)) %>% 
  rename(age = age_group) %>% 
  mutate(age = str_replace_all(age, "Years", "") %>% 
           str_trim) %>% inner_join(classification)
```
